The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-24 paper/ms.tex
van eylen

Beyond searching for planets, \kepler has revolutionized the field of asteroseismology \citep{2010PASP..122..131G}. It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence. \newpage

>>>>

Beyond searching for planets, \kepler has revolutionized the field of asteroseismology \citep{2010PASP..122..131G}. It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence. \newpage
